\section{Methodology}
\label{sec:method}

% ==================== LR START ====================

\subsection{Dataset}
\label{subsec:dataset}

We used the RQ1 subset of the \emph{ImproBR Replication Package},
which is publicly available on Figshare~\cite{akyol2026improbr,improbr2026dataset}.
This subset contains 139 real-world bug reports collected from Mojira,
the official issue tracker for Minecraft. We selected RQ1 because it
provides the report content and manual labels required to evaluate the
executability of \emph{Steps to Reproduce} (S2R).

ImproBR provides two corresponding versions of each issue:
\emph{Raw} and \emph{Improved}. The Raw version preserves the original
report submitted to Mojira before ImproBR processing. The Improved
version contains the output produced by the ImproBR pipeline, in which
components such as S2R may be added, clarified, or reorganized. We
paired the two versions using \texttt{issue\_key}, allowing us to
compare the Raw and Improved reports for the same issue.

We obtained the ground-truth labels from the manual evaluations
included in the replication package
\cite{akyol2026improbr,improbr2026dataset}. In the original study, two
human annotators independently evaluated both versions of each report.
We retained only the S2R label because our study focuses on the
automated assessment of S2R executability.

The S2R label has two possible values: \emph{Executable} and
\emph{Non-Executable}. An Executable label indicates that the
reproduction steps contain sufficient information for an evaluator to
follow them. A Non-Executable label indicates that missing, incorrect,
or ambiguous information prevents the evaluator from completing the
steps without making additional assumptions.

The Raw condition contains 40 Executable reports (28.8\%) and 99
Non-Executable reports (71.2\%). The Improved condition contains 94
Executable reports (67.6\%) and 45 Non-Executable reports (32.4\%). We
used these manual annotations as reference labels when evaluating the
model predictions, matching each prediction to its ground-truth label
using \texttt{issue\_key} and the corresponding report condition.

We evaluated all 139 issues in a single experimental pass under both
the Raw and Improved conditions. We finalized the prompt design and
post-processing rules prior to this evaluation, using a rubric-driven
design process grounded in \path{evaluation_metrics.yaml} rather than
iterative tuning against the evaluation data. We froze the model
version, prompt templates, experiment script, and post-processing
rules before running the configuration, and recorded SHA-256 hashes of
the relevant files to confirm that the configuration remained
unchanged throughout the run. We did not modify any component after
inspecting results.

\subsection{Experimental Setup and Pipeline}
\label{subsec:pipeline}

We implemented the experimental pipeline in Python and used the
\texttt{openai} SDK to access the OpenAI Chat Completions API. We
configured the API to use
\texttt{gpt-4o-mini-2024-07-18}~\cite{openai2024gpt4omini} with
\texttt{temperature}=0 and \texttt{seed}=210. We enabled JSON mode
using \path|response_format={"type":"json_object"}|. The experiment
script did not explicitly set the \texttt{max\_tokens} parameter.

Fixing the model version and generation parameters reduces avoidable
variation between experimental runs and supports replication of the
experimental configuration. However, these settings do not guarantee
identical responses because the API may retain some server-side
nondeterminism.

We created separate prompt templates for the Raw and Improved
conditions. Each template contains a System message and a User
message. The System message defines the model's role, evaluation
rubric, permitted label values, and JSON output requirement. The User
message provides the \texttt{issue\_key}, report content, and required
output schema.

For the Raw condition, the prompt instructs the model to evaluate only
the Raw report. For the Improved condition, the prompt identifies the
Improved report as the evaluation target. It also provides the paired
Raw report as context for interpreting the reporter's original intent.
The complete prompt templates are available in the replication package
because the paper does not have sufficient space to reproduce them in
full.

We derived the post-processing rules from the evaluation rubric prior
to running the evaluation. During inference, the rules inspect the
report under evaluation. For the Improved condition, they may also
inspect the paired Raw report supplied as context. The rules do not
access ground-truth labels or predictions from other issues, and we
did not use any evaluation results to refine the prompts, rules, or
model configuration after the run began.

For each issue, the pipeline reads seven common fields:
\emph{Issue Key}, \emph{Summary}, \emph{Type},
\emph{Affects Version/s}, \emph{Labels}, \emph{Category}, and
\emph{Description}. For the Improved condition, it also reads
\emph{Steps to Reproduce}, \emph{Observed Behavior},
\emph{Expected Behavior}, and \emph{Environment}.

The pipeline excludes ground-truth labels, individual annotator
labels, and previous predictions from the prompt. It also excludes
the following administrative fields: \emph{Confirmation Status},
\emph{Resolution}, \emph{Fix Version/s}, \emph{Votes}, and
\emph{Watch Count}. These exclusions prevent the model from using
information that is not part of the target report content or that may
bias its prediction.

For each Raw issue, the pipeline inserts the Raw report into the Raw
prompt. For each Improved issue, it inserts the Improved report as the
evaluation target and the paired Raw report as original-intent
context. The pipeline sends one application-level API request for each
issue--condition pair. It does not include ground-truth information in
any request. Ground truth is introduced only after prediction, during
metric computation.

We instructed the model to return a structured JSON object. The object
contains \texttt{issue\_key} and the S2R assessment, including the
predicted label, reproducibility, validity, failure type, and
rationale. It also contains auxiliary assessments of Expected Behavior
and Observed Behavior, together with an overall rationale.

The \path{run_experiment.py} script controls the prediction process.
It reads the CSV input, identifies the \texttt{issue\_key}, selects
the appropriate prompt, and constructs the API request. It then calls
the API, parses the response, applies the post-processing rules, and
stores the final prediction.

After receiving a response, the script checks whether the response is
valid JSON. It then verifies the required fields, normalizes
categorical values to the permitted label set, and checks logical
consistency among the returned fields. If the script encounters an API
error, empty response, malformed JSON object, or missing required
field, it records the issue with an \texttt{error} status and proceeds
to the next issue. The script does not implement an additional
application-level retry loop.

The pipeline stores structured predictions in files matching
\path{*_llm_output_*.csv}. It records API metadata separately in files
matching \path{*_api_log_*.csv}. The API logs include the request
status, model version, prompt version, seed,
\texttt{system\_fingerprint}, token usage, and estimated cost.

The source code, prompt templates, configuration hashes, and raw
experimental outputs required to replicate the study are available at
\url{https://github.com/LamSongToan/SWT301_SE1925_G6}.

% ===================== LR END =====================
% ===================== MS START ===================

\subsection{Evaluation Metrics}
\label{subsec:metrics}

We evaluated the model by comparing its predicted S2R label with the
corresponding ground-truth label for each issue and report condition.
We treated Executable as the positive class and Non-Executable as the
negative class. A true positive (\(TP\)) represents an Executable
report correctly predicted as Executable, whereas a true negative
(\(TN\)) represents a Non-Executable report correctly predicted as
Non-Executable. A false positive (\(FP\)) occurs when the model
predicts Executable for a Non-Executable report, and a false negative
(\(FN\)) occurs when the model predicts Non-Executable for an
Executable report.

We used accuracy to measure the proportion of reports for which the
predicted label matches the ground-truth label:

\begin{equation}
\operatorname{Accuracy}
=
\frac{TP+TN}{TP+TN+FP+FN}.
\label{eq:accuracy}
\end{equation}

Although accuracy provides an intuitive measure of correctness, it
does not account for agreement that may occur by chance. It may also
obscure prediction bias when the two classes are unevenly distributed.
We therefore used Cohen's \(\kappa\) as the primary agreement
measure~\cite{cohen1960coefficient}:

\begin{equation}
\kappa
=
\frac{p_o-p_e}{1-p_e},
\label{eq:kappa}
\end{equation}

where \(p_o\) denotes the observed agreement between the model
predictions and ground truth, and \(p_e\) denotes the agreement
expected by chance from their marginal label distributions. A value
of \(\kappa=1\) indicates perfect agreement, whereas
\(\kappa=0\) indicates agreement equivalent to chance. A negative
value indicates agreement below the chance level.

The experimental protocol defined \(\kappa \geq 0.70\) as the
acceptance threshold before the Holdout evaluation. We used this value
as a project-specific decision criterion rather than as a universal
boundary for model quality. We interpreted kappa together with
accuracy, the confusion matrix, and the prediction distribution.

For each condition, the confusion matrix reports \(TP\), \(TN\),
\(FP\), and \(FN\). We also recorded the number and identities of
mismatched cases to determine whether errors primarily resulted from
overpredicting Executable or overpredicting Non-Executable. This
mismatch analysis was descriptive and did not modify the frozen
configuration.

The \path{compute_metric.py} script calculates accuracy, Cohen's
kappa, the confusion matrix, and the mismatch list separately for the
Raw and Improved conditions. It produces \path{summary_*.csv} files
containing aggregate metrics and \path{mismatch_analysis_*.csv} files
containing issue-level errors. The
\path{compare_raw_improved.py} script places the Raw and Improved
results side by side for each experimental phase.

Metrics from Pilot, Development, and Pilot Validation describe
configuration development and calibration. We based the final
assessment of model performance only on the protected Holdout subset.

\subsection{Statistical Analysis}
\label{subsec:statistics}

We used \texttt{issue\_key} as the unit of analysis. Because each
issue has paired Raw and Improved versions, all comparisons preserve
the correspondence between the two report conditions.

We restricted the final analysis to the 38 issues in the protected
Holdout subset. For each condition, we reported the exact number of
correct and incorrect predictions, accuracy, Cohen's kappa, the
confusion matrix, and the prediction distribution. We used the Pilot,
Development, and Pilot Validation results only for procedural checks,
configuration refinement, and descriptive analysis.

The current analysis compares the Raw and Improved conditions
descriptively. Specifically, \path{compare_raw_improved.py} reports
their metric values side by side but does not implement a hypothesis
test, confidence interval, or inferential effect-size estimate.
Accordingly, we do not report \(p\)-values or claim that an observed
difference between the two conditions is statistically significant.
We interpret the results using their exact counts, accuracy, kappa,
confusion matrices, and observed error patterns.

We did not use Holdout predictions or mismatches to revise the prompt,
post-processing rules, model parameters, or evaluation code after the
frozen Holdout run.

% ===================== MS END =====================
