\section{Threats to Validity}
\label{sec:threats}

\subsection{Internal Validity}
 
The primary threat is \emph{model non-determinism between runs or versions}. We mitigate this by using a fixed model snapshot (\texttt{gpt-4o-mini-2024-07-18} rather than a model alias), setting temperature to 0 for deterministic generation, and locking the prompt template to a single version throughout all 139 reports.
 
Another threat is \emph{prompt design bias}, where the wording could inadvertently shift the LLM's scoring behavior. We reduce this through a clearly defined ordinal rubric (scale 1--5), and we use a controlled fallback strategy (zero-shot $\to$ few-shot only under predefined pilot conditions) rather than iterative prompt refinement.
 
\subsection{Construct Validity}
 
A key concern is whether we are truly measuring ``reproducibility.'' Potential threats include misalignment between how humans and LLMs interpret reproducibility, and dependence on structured extraction (Steps to Reproduce, Expected/Observed Behavior) that may introduce abstraction bias.
 
We address this by anchoring the LLM rubric to the existing human annotation guidelines in the dataset, using the same ordinal scale for both human and LLM evaluation, and analyzing agreement separately for each reproducibility dimension (Steps, Observed Behavior, Expected Behavior) to reduce over-abstraction from a single composite score. Running the identical pipeline on both the Raw and Improved forms further guards against a construct threat specific to LLM evaluators: because the Improved form differs from Raw mainly in surface fluency rather than in the ground-truth construct, the sharp drop in agreement on Improved is evidence that the model partly responds to presentation rather than reproducibility itself---a threat we surface rather than hide.
 
\subsection{External Validity}
 
The study is limited to Mojira Minecraft bug reports, an open-source game development context. Results may not generalize to enterprise bug tracking systems or other domains with different reporting standards. The Improved form is also specific to one improvement pipeline (ImproBR); a different rewriting system might induce a different bias, though the mechanism we identify---an evaluator over-crediting fluent, complete-looking text---is not specific to ImproBR.
 
However, the dataset spans diverse technical bug types and is directly comparable to prior OSS studies, and evaluating both the original and the AI-improved form strengthens external validity relative to a single-form study: it shows the protocol applies to machine-rewritten reports and quantifies how much agreement changes between the two. The measurement protocol itself is domain-agnostic and can be replicated on other issue trackers and other improvement pipelines.
 
\subsection{Conclusion Validity}
 
Cohen's Kappa can be sensitive to class imbalance in ordinal scores, and bootstrap confidence intervals may fluctuate depending on resampling variance. The Wilcoxon signed-rank test assumes symmetric pair-wise differences.
 
We mitigate these by computing bootstrap confidence intervals for $\kappa$ rather than relying on asymptotic assumptions, using non-parametric Wilcoxon testing (appropriate for ordinal data), and reporting effect sizes (rank-biserial correlation) alongside $p$-values.
 
\subsection{Reproducibility}
 
To ensure our results are reproducible, we fix the datasets to the 139 Raw and 139 Improved Mojira reports, pin the model version explicitly, lock one fixed prompt template per form (held identical between pilot and full run), remove randomness from sampling, and use standard statistical libraries (scikit-learn, scipy).
 