\section{Conclusion}
\label{sec:conclusion}

This study measures how closely an LLM-based reproducibility evaluator
(GPT-4o mini) agrees with human judgment on the ImproBR replication package,
which provides two co-equal forms of the same 139 Mojira Minecraft bug reports:
the original \emph{Raw} reports and their LLM-rewritten \emph{Improved} versions.
Using a single deterministic scoring function applied to both human annotations
and LLM output, and Cohen's kappa against a pre-registered threshold of
$\kappa \geq 0.70$, we run the identical evaluation on each form and compare.

On the Raw form the model reaches $\kappa = 0.578$---below the threshold but
close to the $\kappa_{\text{control}} = 0.674$ between the two human annotators,
with no systematic bias. On the Improved form agreement falls to
$\kappa = 0.335$, far below the human ceiling on those reports ($0.556$), driven
by a significant optimistic bias: the model scores higher than the human in 47
of 52 disagreements and calls 111 of 139 reports reproducible. The degradation
is concentrated in the free-text Observed and Expected Behavior dimensions and
is small on the structural Steps to Reproduce dimension (Raw $\kappa = 0.693$,
Improved $0.654$); a coarse reproducible/not check stays high on both forms
($87.1\%$ and $86.3\%$). The headline of the study is the contrast: the same
evaluator that nearly matches human agreement on original reports is
systematically misled by reports another LLM has polished.

Taken together, GPT-4o mini is not yet reliable enough to replace human
reproducibility review on either form, and it is markedly less reliable on
AI-improved reports than on original ones. It could realistically serve as a
human-supervised coarse pre-filter today, but any deployment that scores
LLM-generated or LLM-rewritten text must expect an optimistic bias and validate
the evaluator on that kind of text specifically.

Future work should (i) target prompt or rubric refinement at the Observed and
Expected Behavior dimensions, which are both the weakest and the ones most
affected by the model crediting fluent text; (ii) test whether stricter
grounding instructions or few-shot examples reduce the optimistic bias on
AI-improved reports without harming Raw agreement; and (iii) replicate the
protocol on additional issue trackers and additional improvement pipelines, to
test whether the Raw-vs-Improved agreement gap observed here generalizes beyond
Mojira/Minecraft and beyond ImproBR.
